### 2021-06-18 manuscript.tex
update

\emph{Oliveira, C. F. ; Lopez, S. R. ; Tran, Q. A. ; Breul, P. ; Canou, J. ; Reiffsteck, P. ; Dupla, J. C. ; Jacquard, C. ; Teyssier, A. ; Benz-Navarrete, M. A. Soil modulus assessment by means of cone dynamic loading test. 20th International Conference on Soil Mechanics and Geotechnical Engineering (ICSMGE), Sydney, May 2022. (Présentation orale - Résumé accepté)}\\[0.01cm]

>>>>

\emph{Oliveira, C. F. ; Benz-Navarrete, M. A. ; Breul, P. ; Tran, Q. A. ; Chevalier, B. ; Bacconnet, C. Assessment of small-strain modulus through wave velocity measurement with dynamic penetrometer Panda 3®. 6th International Confe- rence on Geotechnical and Geophysical Site Characterization, Budapest, Sep- tembre 2021. (Présentation orale).}
